Two NIRCam channels are Better than One: How JWST Can Do More Science with NIRCam's Short-Wavelength Dispersed Hartmann Sensor

### 2016-08-25 ms.tex
I updated the plural/singular info for all the cases of the word 'data' I could find, as Marcia caught me using 'data' as a singular.

The NIRCam instrument can reduce the number of transits needed to build up a 1$\mu$m to 5$\mu$m transmission or emission spectrum of a planet.
This is because the instrument has a dichroic that splits the incoming beam into a short-wavelength channel and long-wavelength channel, so simultaneous imaging and/or spectroscopy are possible at short ($<$2.4$\mu$m) and long ($>$2.4$\mu$m) wavelengths.
In principle, the DHS can be used to simultaneously cover 1.0$\mu$m to 2.0$\mu$m while the long-wavelength grisms cover either 2.44$\mu$m to 4.02$\mu$m (with the F322W2 filter) or 3.88$\mu$m to 4.98$\mu$m (with the F444W) filter.
Thus, the DHS data comes ``for free'' with any long-wavelength NIRCam grism data, aside from readout and data rate considerations discussed in Section \ref{sec:readout}.
For the example above of HD 209458b, simultaneous DHS data would reduce the required transits from four to three, saving about 11 JWST hours 
if the wavelengths from 2.0$\mu$m to 2.4$\mu$m and higher Signal to Noise ratios (SNRs) from NIRISS are not required.
The DHS is expected to collect similar photon levels as HST's WFC3 grisms, so it is like a free coordinated HST observation for every long-wavelength NIRCam grism transit.

@@

\begin{figure*}[!thb]
\centering
\subfloat[HD 209458b]{
	\includegraphics[width=0.5\textwidth]{molecules_DHS_HD209.pdf}
	%\caption{HD209458b}
	\label{fig:209spec}
	}
\subfloat[HAT-P-12b]{
	\includegraphics[width=0.5\textwidth]{HAT-P-12b_kmr_cloudy_dhs.pdf}
	%\caption{HAT-P-12b}
	\label{fig:HATp12spec}
	}
	\caption{Model spectra separated by molecule for HD~209458b and the inflated warm Saturn HAT-P-12b.The new DHS mode would allow simultaneous spectra at 1-2$\mu$m ``for free'' when observing with either NIRCam's F322W2 or F444W slitless grism observations in its long-wavelength channel. a) The simulated data for HD~209458b consists of one transit in each of the long-wavelength grism modes, each accompanied by simultaneous DHS grism spectra. The observations longer than 5$\mu$m are simulated for MIRI's Low Resolution Spectrometer. b) HAT-P-12b is an inflated warm Saturn with an opaque cloud deck at 1 mbar. Error bars shown are for simulated observation with the DHS grism, F322W2 and F444W modes, consisting of a total of 2 transits or about 17 hours of JWST time. A planet metallicity of 22~$\times$~solar was assumed from the relation in \citet{kreidberg2014wasp43}}
	\label{fig:spec}
\end{figure*}

>>>>

The NIRCam instrument can reduce the number of transits needed to build up a 1$\mu$m to 5$\mu$m transmission or emission spectrum of a planet.
This is because the instrument has a dichroic that splits the incoming beam into a short-wavelength channel and long-wavelength channel, so simultaneous imaging and/or spectroscopy are possible at short ($<$2.4$\mu$m) and long ($>$2.4$\mu$m) wavelengths.
In principle, the DHS can be used to simultaneously cover 1.0$\mu$m to 2.0$\mu$m while the long-wavelength grisms cover either 2.44$\mu$m to 4.02$\mu$m (with the F322W2 filter) or 3.88$\mu$m to 4.98$\mu$m (with the F444W) filter.
Thus, the DHS data come ``for free'' with any long-wavelength NIRCam grism data, aside from readout and data rate considerations discussed in Section \ref{sec:readout}.
For the example above of HD 209458b, simultaneous DHS data would reduce the required transits from four to three, saving about 11 JWST hours 
if the wavelengths from 2.0$\mu$m to 2.4$\mu$m and higher Signal to Noise ratios (SNRs) from NIRISS are not required.
The DHS is expected to collect similar photon levels as HST's WFC3 grisms, so it is like a free coordinated HST observation for every long-wavelength NIRCam grism transit.

@@

\begin{figure*}[!thb]
\centering
\subfloat[HD 209458b]{
	\includegraphics[width=0.5\textwidth]{molecules_DHS_HD209.pdf}
	%\caption{HD209458b}
	\label{fig:209spec}
	}
\subfloat[HAT-P-12b]{
	\includegraphics[width=0.5\textwidth]{HAT-P-12b_kmr_cloudy_dhs.pdf}
	%\caption{HAT-P-12b}
	\label{fig:HATp12spec}
	}
	\caption{Model spectra separated by molecule for HD~209458b and the inflated warm Saturn HAT-P-12b.The new DHS mode would allow simultaneous spectra at 1-2$\mu$m ``for free'' when observing with either NIRCam's F322W2 or F444W slitless grism observations in its long-wavelength channel. a) The simulated data for HD~209458b consist of one transit in each of the long-wavelength grism modes, each accompanied by simultaneous DHS grism spectra. The observations longer than 5$\mu$m are simulated for MIRI's Low Resolution Spectrometer. b) HAT-P-12b is an inflated warm Saturn with an opaque cloud deck at 1 mbar. Error bars shown are for simulated observation with the DHS grism, F322W2 and F444W modes, consisting of a total of 2 transits or about 17 hours of JWST time. A planet metallicity of 22~$\times$~solar was assumed from the relation in \citet{kreidberg2014wasp43}}
	\label{fig:spec}
\end{figure*}
